Theories of deliberated choice

### 2024-01-15 simple.tex
C^HA

  \begin{theorem}
    \label{th:suffIndic}
    Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
    Then, there exists a claim that holds and is anonymous and indicative.
  \end{theorem}
  \begin{proof}
    Define $p = P_{i_1}$.
    Define the claim as $\forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}$.
    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
    The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
  \end{proof}
  \begin{corollary}
    \label{th:suffIndicDec}
    Assume that for some $p \in P$, we have $\exists i \in I \suchthat P_i = p$ and $\forall i_2 \suchthat P_{i_2} \neq p$ we have that $\exists A \in \finite(\allargs) \suchthat \forall i \in I \suchthat P_i \neq p, \exists a \in A \suchthat {\ileadstost}(a) \in P \setminus \set{p}$, then there exists a claim that holds and is anonymous and indicative.
  \end{corollary}
  \begin{proof}
    We know that $i_1$ has some decisive argument $a_1$ in favor of $p$.
    Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
    Apply \cref{th:suffIndic}.
  \end{proof}

>>>>

  Define the claim $C^\text{HA} = \set{{\allleadsto} \circ \sigma \suchthat \sigma: I \Leftrightarrow I}$, or equivalently, $C^\text{HA} = \set{{\allleadstog} \in \allleadstos \suchthat \forall f \in P^{\allhists}: \card({\allleadstoginv}(f)) = \card({\allleadstoinv}(f))}$.
  Under anonymity, requesting that a claim holds is the same as requesting that it includes $C^\text{HA}$.
  \begin{theorem}
    \label{th:claim_ha}
    A claim holds and is anonymous iff it includes $C^\text{HA}$ and is anonymous.
    In particular, $C^\text{HA}$ holds and is anonymous.
  \end{theorem}
\begin{remark}
  Define $C^\text{A} = \set{{\allleadstog} \in \allleadstos \suchthat {\allleadstog}(I) \wsub {\allleadsto}(I)}$. Observe that $C^\text{A}$ is anonymous, that $C^\text{HA} \wsub C^\text{A}$, and that $C^\text{HA} \neq C^\text{A}$ iff $\forall i, j \in I: {\ileadsto} \neq {\ileadsto[j]}$.
\end{remark}

  \begin{theorem}
    \label{th:suffIndic}
    Assume that for some $H \in \finite(\incr(\allhists))$ and $i_1 \in I \suchthat P_{i_1} \in P$, we have $\forall i_2 \suchthat P_{i_2} \neq P_{i_1}$ that $\exists \hist \in H \suchthat {\allleadsto}(\hist, i_1) \neq {\allleadsto}(\hist, i_2)$.
    Then, there exists a claim that holds and is anonymous and indicative.
  \end{theorem}
  \begin{proof}
    Define $p = P_{i_1}$.
    Consider any claim $C$ such that $C^\text{HA} \wsub C \wsub C^\text{A}$ and $C$ is anonymous.
    % Define the claim $C$ as $\set{{\allleadstog} \in \allleadstos \suchthat \forall i \in I: {\ileadstog} \in \set{{\ileadsto[j]} \suchthat j \in I}}$ (or as anything included in it that includes $C^\text{HA}$ and is anonymous).
    The claim is indicative for $i = i_1$ and $\theta = \set{(\hist, i_1, {\allleadsto}(\hist, i_1)) \suchthat \hist \in H}$ for the following reason.
    The attitudes in $C$ compatible with $\theta$ are $\set{{\allleadstog} \suchthat \theta \wsub {\allleadstog}} \cap C \wsub \set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}}$, and $\pi(\set{{\allleadstog} \suchthat {\ileadstog[i_1]} \in \set{{\ileadsto[j]} \suchthat P_j = p}})(i_1) = p$.
  \end{proof}
  \begin{corollary}
    \label{th:suffIndicDec}
    Assume that for some $p \in P$, we have $\exists i \in I \suchthat P_i = p$ and $\forall i_2 \suchthat P_{i_2} \neq p$ we have that $\exists A \in \finite(\allargs) \suchthat \forall i \in I \suchthat P_i \neq p, \exists a \in A \suchthat {\ileadstost}(a) \in P \setminus \set{p}$, then there exists a claim that holds and is anonymous and indicative.
  \end{corollary}
  \begin{proof}
    We know that $i_1$ has some decisive argument $a_1$ in favor of $p$.
    Assume (wlog) that $A = \set{2, …, \card{A} + 1}$.
    Define $\hist_1 = \emptyset$ and for $i \in \intvl{2, \card{A} + 1}$, $\hist_i = (\hist_{i - 1}, a_1, i)$.
    Define $H = \set{\hist_i \suchthat i \in \intvl{2, \card{A} + 1}}$.
    Apply \cref{th:suffIndic}.
  \end{proof}

\begin{conjecture}
  The converse of \cref{th:suffIndic} holds.
\end{conjecture}
\begin{proof}
  HA requires that the claim includes at least $C^\text{HA}$.
  Indicativenes requires a $\theta$ that keeps a single type $i_1$ and rejects all $i_2$ (those with a deliberated judgment different from $i_1$).
  Can we build a suitable $H$ with that $\theta$?
  The question is: can we have $\theta$ about two individuals but still single out a single type?
  Yes: claim is that all individuals reason in the same way about a given $\hist$.
  In such a case, the observations about $i_2$, $i_3$ permit to know that the world is such that my observations about $i_1$ (if any) permit to single it out. 
  In such a case, I conjecture that as the claim holds, adding those observations about $i_2$, $i_3$, we obtain a set of possible worlds which contain the real one; out of this we can build $H$ using the observations in $\theta$.
  In other words, from $\theta$, consider only the observations about $i_1$ and define $H$ using those. Prove that this singles out $i_1$, from the fact that the world conforms to the remaining observations (about $i_2$, $i_3$) in $\theta$.
\end{proof}
